\Large \bf On semidefinite-representable sets over valuation fields

### 2025-05-23 article/paper_padic_spec.tex
commit by Simone

The study of polyhedra and of linear programming (LP) is at the heart of convex geometry and optimization,
inasmuch as several optimization problems can be cast as, or reduced to LP. An important generalization of LP
is semidefinite programming (SDP), namely the problem of minimizing an affine polynomial over the set of
positive semidefinite affine combinations of a given collection of real symmetric matrices. The latter problem 
has interested the community of polynomial optimization because of the relaxation method known as moment-SOS
(or Lasserre) hierarchy \cite{henrion2020moment}.

@@

In this paper we consider the situation where input data are defined over fields $K$ with a prescribed valuation map $\val$ on $K$. The main example is the field of $p$-adic numbers with $p$-adic valuation. Similar generalizations have been recently proposed in the context of tropical geometry \cite{iriarte2022polyhedral} and tropical methods applied to non-archimedean semidefinite programming \cite{allamigeon2016solving,allamigeon_tropical_2020}.

>>>>

The study of polyhedra and of linear programming (LP) is at the heart of convex geometry and optimization,
inasmuch as several optimization problems can be cast as, or relaxed to LP. An important generalization of LP
is semidefinite programming (SDP), namely the problem of minimizing an affine polynomial over the set of
positive semidefinite affine combinations of a given collection of real symmetric matrices. The latter problem 
has interested the community of real algebraic geometry and polynomial optimization, mostly because of the
relaxation method known as moment-SOS (or Lasserre) hierarchy \cite{henrion2020moment}.

@@

In this paper we consider the situation where input data are defined over fields $K$ with a prescribed valuation map $\val$ on $K$. The main example is the field of $p$-adic numbers with $p$-adic valuation.

POLYHEDRA

SPECTRAHEDRA
Similar generalizations have been recently proposed in the context of tropical geometry \cite{iriarte2022polyhedral} and tropical methods applied to non-archimedean semidefinite programming \cite{allamigeon2016solving,allamigeon_tropical_2020}.
